### 2017-02-01 local-capability-machine.tex

\subsubsection{Downward closedness lemmas}
\label{sec:downward-closedness}

\begin{lemma}[$\mathit{writeCondition}$ downwards-closed]
  \label{lem:writecond-dc}
  \begin{itemize}
  \item $n' \leq n$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{(\nwl,p)}\}$
  \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:writecond-dc}]
  % TODO
\end{proof}

\begin{lemma}[$\mathit{execCondition}$ downwards-closed]
  \label{lem:execcond-dc}
  \begin{itemize}
  \item $n' \leq n$
  \item $\perm \in \{\exec, \rwx, \rwlx\}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-dc}]
  % TODO
\end{proof}

\begin{lemma}[$\mathit{enterCondition}$ downwards-closed]
  \label{lem:entrycond-dc}
  \begin{itemize}
  \item $n' \leq n$
  \item $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\addr,\start,\addrend)} \in \entryCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:entrycond-dc}]
  % TODO
\end{proof}

\begin{lemma}[$\stdvr{\cdot}$ downwards-closed]
  \label{lem:stdvr-dc}
  \begin{itemize}
  \item $n' \leq n$
  \item $\npair{\word} \in \stdvr(W)$
  \end{itemize}
  then 
  \[
   \npair[n']{\word} \in \stdvr(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stdvr-dc}]
  % TODO
\end{proof}

\begin{lemma}[$\stdrr{\cdot}$ downwards-closed]
  \label{lem:stdrr-dc}
  \begin{itemize}
  \item $n' \leq n$
  \item $\npair{\reg} \in \stdrr(W)$
  \end{itemize}
  then 
  \[
   \npair[n']{\reg} \in \stdrr(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stdrr-dc}]
  % TODO
\end{proof}

\begin{lemma}[Heap satisfaction downwards closure]
  \label{lem:heap-sat-dc}
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

\subsubsection{Monotonicity lemmas}
\label{sec:mono}

\begin{lemma}[$\mathit{readCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:readcond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\npair{(\start,\addrend)} \in \readCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:readcond-mono-priv}]
  % TODO
\end{proof}

\begin{lemma}[$\mathit{execCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:execcond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\perm \in \{\exec, \rwx \}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\perm,\start,\addrend)}\in \execCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-mono-priv}]
  % TODO
\end{proof}

\begin{lemma}[$\mathit{enterCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:entrycond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\addr,\start,\addrend)}\in \entryCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-mono-priv}]
  % TODO
\end{proof}

@@

@@

\begin{lemma}[Conditions for load instruction are sufficient]
  \label{lem:conds-load-suffice}
  If
  \begin{itemize}
  \item $\heapSat[\memheap]{n}{W}$
  \item $\var{c} = ((\perm,\gl),\start,\addrend,\addr)$
  \item $\npair{c}\in\stdvr(W)$
  \item $\readAllowed{\perm}$ 
  \item $\withinBounds{\var{c}}$
  \end{itemize}

  then $\npair[n-1]{\memheap(\addr)} \in \stdvr(W)$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item $\npair{(\start,\addrend)} \in \readCond{\gl}(W)$: follows by
    definition of $\stdvr{\cdot}$ from $\npair{c}\in\stdvr(W)$.
  \item $\exists r \in \var{localityReg}(g,W)$, $[\start',\addrend'] \supseteq
    [\start,\addrend] \ldotp$ $W(r)\nsubsim[n-1]
    \iota_{\start',\addrend'}^\pwl$. By definition of $\readCond{\gl}(W)$. \label{step:unfold-readCond}
  \item $\exists P : \activeReg{W} \rightarrow \HeapSegments \ldotp
    \memSatPar{\memheap}{W}{P}$. By definition of $\heapSat[\memheap]{n}{W}$.
  \item $\memheap = \biguplus_{r\in\activeReg{W}}P(r)$ and $\forall r \in
    \activeReg{W}$, $n'<n \ldotp$ $\exists H,s \ldotp$ $W(r) = (\_,s,\_,\_,H)$
    and $\npair[n']{P(r)} \in H(s)(\xi^{-1}(W))$. By definition of
    $\memSatPar{\memheap}{W}{P}$. \label{step:unfold-phi-sat-part}
  \item $r \in \var{localityReg}(g,W)\subseteq \activeReg{W}$. By definition of
    $\var{localityReg}(\cdot)$ and $\activeReg{\cdot}$.
  \item $\exists H,s \ldotp$ $W(r) = (\_,s,\_,\_,H)$
    and $\npair[n-1]{P(r)} \in H(s)(\xi^{-1}(W))$.
    By specializing the result from
    Step~\ref{step:unfold-phi-sat-part} to the $r$ from
    Step~\ref{step:unfold-readCond} and $n' = n-1$.
  \item $\npair[n-1]{P(r)} \in H^\pwl_{\start',\addrend'}(s)(\xi^{-1}(W))$.
    Follows by combining $\npair[n-1]{P(r)} \in H(s)(\xi^{-1}(W))$ with
    $W(r)\nsubsim[n-1] \iota_{\start',\addrend'}^\pwl$ from Step~\ref{step:unfold-readCond}.
  \item $\dom(P(r)) = [\start',\addrend']$ and for all $\addr' \in
    [\start',\addrend']\ldotp$
    $\npair[n-2]{P(r)(\addr')}\in\stdvr(\xi(\xi^{-1}(W)))$.
  \item $\addr \in [\start,\addrend]\subseteq[\start',\addrend']$. By combining
    $\withinBounds(c)$ with the fact that $[\start',\addrend'] \supseteq
    [\start,\addrend] \ldotp$ from Step~\ref{step:unfold-readCond}.
  \item In particular, we get: $\memheap(\addr) = P(r)(\addr)$ and
    $\npair[n-2]{P(r)(\addr)}\in\stdvr(W)$.
  \end{enumproof}
\end{proof}

@@

@@

\begin{lemma}
  \begin{align*}
    &\forall n,W_1,W_2,W_1' \ldotp
    &\quad W_1 \nequal W_2 \land W_1' \futurewk W_1 \Rightarrow \exists W_2' \ldotp W_2' \nequal W_1' \land W_2' \futurewk W_2
  \end{align*}
\end{lemma}

\begin{lemma}
  \begin{align*}
    &\forall n,W_1,W_2,W_1' \ldotp
    &\quad W_1 \nequal W_2 \land W_1' \futurestr W_1 \Rightarrow \exists W_2' \ldotp W_2' \nequal W_1' \land W' \futurestr W_2
  \end{align*}
\end{lemma}

>>>>

@@

\begin{lemma}[$\mathit{readCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:readcond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\npair{(\start,\addrend)} \in \readCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:readcond-mono-priv}]
  $\readCond{}(\glob)(W)$ picks a $\perma$ region from $W$. $\perma$ regions are persistent over $\futurestr$, so we can use the region that the assumption gives us.
\end{proof}

\begin{lemma}[$\mathit{writeCondition}$ downwards-closed]
  \label{lem:writecond-dc}
  If 
  \begin{itemize}
  \item $n' \leq n$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{(\nwl,p)}\}$
  \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:writecond-dc}]
  $\writeCond{}(\iota,\glob)(W)$ picks a $\perma$ region from $W$. $\perma$ regions are persistent over $\futurestr$, so we can use the region that the assumption gives us.
\end{proof}

\begin{lemma}[$\mathit{execCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:execcond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\perm \in \{\exec, \rwx \}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\perm,\start,\addrend)}\in \execCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-mono-priv}]
  Assume $W_2 \futurestr W_1$, $\perm \in \{\exec, \rwx \}$ and $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W_1)$. Now let $W_3 \futurestr W_2$, $\addr \in [\start,\addrend]$, and $n' < n$, and show
  \[
    \npair{\stdcap[(\perm,\glob)]} \in \stder(W_3)
  \]
  by transitivity we have $W_3 \futurestr W_1$, so the result follows from $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W_1)$.
\end{proof}

\begin{lemma}[$\mathit{execCondition}$ downwards-closed]
  \label{lem:execcond-dc}
  If
  \begin{itemize}
  \item $n' \leq n$
  \item $\perm \in \{\exec, \rwx, \rwlx\}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-dc}]
  % TODO
\end{proof}

\begin{lemma}[$\mathit{enterCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:entrycond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\addr,\start,\addrend)}\in \entryCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:entrycond-mono-priv}]
  Assume $W_2 \futurestr W_1$ and $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\glob)(W_1)$. Now let $W_3 \futurestr W_2$, $n' < n$, and show
  \[
    \npair{\stdcap[(\exec,\glob)]} \in \stder(W_3)
  \]
  by transitivity we have $W_3 \futurestr W_1$, so the result follows from $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\glob)(W_1)$.
\end{proof}

\begin{lemma}[$\mathit{enterCondition}$ downwards-closed]
  \label{lem:entrycond-dc}
  If
  \begin{itemize}
  \item $n' \leq n$
  \item $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\addr,\start,\addrend)} \in \entryCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:entrycond-dc}]
  % TODO
\end{proof}

\subsubsection{LR Sanity lemmas}

\begin{lemma}[Heap satisfaction downwards closure]
  \label{heap-sat-dc}
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Conditions for load instruction are sufficient]
  \label{lem:conds-load-suffice}
  \item $\heapSat[\memheap]{n}{W}$
  \item $\var{c} = ((\perm,\gl),\start,\addrend,\addr)$
  \item $\npair{c}\in\stdvr(W)$
  \item $\readAllowed{\perm}$ 
  \item $\withinBounds{\var{c}}$
  then $\npair[n-1]{\memheap(\addr)} \in \stdvr(W)$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item $\npair{(\start,\addrend)} \in \readCond{\gl}(W)$: follows by
    definition of $\stdvr{\cdot}$ from $\npair{c}\in\stdvr(W)$.
  \item $\exists r \in \var{localityReg}(g,W)$, $[\start',\addrend'] \supseteq
    [\start,\addrend] \ldotp$ $W(r)\nsubsim[n-1]
    \iota_{\start',\addrend'}^\pwl$. By definition of $\readCond{\gl}(W)$. \label{step:unfold-readCond}
  \item $\exists P : \activeReg{W} \rightarrow \HeapSegments \ldotp
    \memSatPar{\memheap}{W}{P}$. By definition of $\heapSat[\memheap]{n}{W}$.
  \item $\memheap = \biguplus_{r\in\activeReg{W}}P(r)$ and $\forall r \in
    \activeReg{W}$, $n'<n \ldotp$ $\exists H,s \ldotp$ $W(r) = (\_,s,\_,\_,H)$
    and $\npair[n']{P(r)} \in H(s)(\xi^{-1}(W))$. By definition of
    $\memSatPar{\memheap}{W}{P}$. \label{step:unfold-phi-sat-part}
  \item $r \in \var{localityReg}(g,W)\subseteq \activeReg{W}$. By definition of
    $\var{localityReg}(\cdot)$ and $\activeReg{\cdot}$.
  \item $\exists H,s \ldotp$ $W(r) = (\_,s,\_,\_,H)$
    and $\npair[n-1]{P(r)} \in H(s)(\xi^{-1}(W))$.
    By specializing the result from
    Step~\ref{step:unfold-phi-sat-part} to the $r$ from
    Step~\ref{step:unfold-readCond} and $n' = n-1$.
  \item $\npair[n-1]{P(r)} \in H^\pwl_{\start',\addrend'}(s)(\xi^{-1}(W))$.
    Follows by combining $\npair[n-1]{P(r)} \in H(s)(\xi^{-1}(W))$ with
    $W(r)\nsubsim[n-1] \iota_{\start',\addrend'}^\pwl$ from Step~\ref{step:unfold-readCond}.
  \item $\dom(P(r)) = [\start',\addrend']$ and for all $\addr' \in
    [\start',\addrend']\ldotp$
    $\npair[n-2]{P(r)(\addr')}\in\stdvr(\xi(\xi^{-1}(W)))$.
  \item $\addr \in [\start,\addrend]\subseteq[\start',\addrend']$. By combining
    $\withinBounds(c)$ with the fact that $[\start',\addrend'] \supseteq
    [\start,\addrend] \ldotp$ from Step~\ref{step:unfold-readCond}.
  \item In particular, we get: $\memheap(\addr) = P(r)(\addr)$ and
    $\npair[n-2]{P(r)(\addr)}\in\stdvr(W)$.
  \end{enumproof}
\end{proof}

@@

\begin{lemma}[Fundamental theorem proof helper lemma]
  \label{lem:ftlr-induction-helper}
  For all $n$, $\perm$, $\start$, $\addrend$, $\addr$, $\gl$, $W$  \\
  If one of the following holds:
  \begin{itemize}
  \item \[
      \begin{gathered}
        \perm = \exec \land\\
        \npair{(\start,\addrend)} \in \readCond{}(\gl)(W)
      \end{gathered}
    \]
  \item \[
      \begin{gathered}
        \perm = \rwx \land \\
        \npair{(\start,\addrend)} \in \readCond{}(\gl)(W) \land\\
        \npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W)
      \end{gathered}
    \]
  \item \[
      \begin{gathered}
        \perm = \rwlx \land\\
        \npair{(\start,\addrend)} \in \readCond{}(\gl)(W) \land\\
        \npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W),
      \end{gathered}
    \]
  \end{itemize}
  and
  \begin{itemize}
  \item $\npair[n]{\reg}\in \stdrr(W)$
  \item $\heapSat[\hs]{n}{W}$
  \item $i \leq n$
  \item $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f) \step[i] (\halted,\Phi)$
  \end{itemize}

  Then $\exists W' \futurestr W$, $\hs_r$, $\hs' \ldotp$
  $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and $\heapSat[\hs']{n-i}{W'}$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item By induction on $n$. In other words, assume that the theorem already
    holds for all $n' < n$.
  \item $i \neq 0$, since
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
    \ms_f)\neq (\halted,\Phi)$ for any $\Phi$. \\
    Therefore, assume w.l.o.g. that $i = 1+i'$,
    \begin{equation*}
      (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f) \step \var{conf'} \step[i'] (\halted,\Phi)
    \end{equation*}
  \item $\start \leq \addr \leq \addrend$, $\perm \in \{ \exec,\rwx, \rwlx \}$
    and $\var{conf'} =
    \sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
    \uplus \ms_f))$\\
    By definition of
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f)
    \step \var{conf'}$, using the fact that $\var{conf'} \neq \failed$ (since it
    is not possible that $\failed \step[i'] (\halted,\Phi)$)
  \item We do a case analysis on
    $\memheap(a)$
    \begin{enumproof}
    \item Case $\memheap(a) = \jmp{\lv}$:
    \item Case $\memheap(a) = \jnz{\lv}{\rv}$:
    \item Case $\memheap(a) = \move{\lv}{\rv}$:
    \item Case $\memheap(a) = \load{\lv}{\hv}$:
    \item Case $\memheap(a) = \store{\hv}{\rv}$:
    \item Case $\memheap(a) = \plus{\lv}{\rv}{\rv}$:
    \item Case $\memheap(a) = \lea{\lv}{\rv}$:
    \item Case $\memheap(a) = \restricttwo{\lv}{\rv}$:
    \item Case $\memheap(a) = \subseg{\lv}{\rv}{\rv}$:
    \item Case $\memheap(a) = \isptr{\lv}{\rv}$:
    \item Case $\memheap(a) = \getp{\lv}{\lv}$:
    \item Case $\memheap(a) = \getl{\lv}{\lv}$:
    \item Case $\memheap(a) = \getb{\lv}{\lv}$:
    \item Case $\memheap(a) = \gete{\lv}{\lv}$:
    \item Case $\memheap(a) = \geta{\lv}{\lv}$:
    \item Case $\memheap(a) = \fail$: Contradiction, since then
      $\sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
      \uplus \ms_f)) = \failed$, so we have that $\failed \step[i']
      (\halted,\Phi)$ which is not possible.
    \item Case $\memheap(a) = \halt$:
      \begin{enumproof}
      \item
        $\sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
        \uplus \ms_f)) = (\halted, (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
        \uplus \ms_f))$\\
        By definition of $\sem{\cdot}$
      \item Then $i' = 0$ and $\Phi =
        (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
        \ms_f)$. Follows from $(\halted,
        (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
        \ms_f)) \step[i'] (\halted,\Phi)$
      \item For $W' = W$, $\ms_r = \emptyset$ and $\ms' = \ms$, we have that
        $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and
        $\heapSat[\hs']{n-1}{W'}$ (using Lemma~\ref{heap-sat-dc}).
      \end{enumproof}
    \end{enumproof}
  \end{enumproof}
\end{proof}

@@

\begin{lemma}
  \label{lem:wk-nequal-and-future}
  \begin{align*}
    &\forall n,W_1,W_2,W_1' \ldotp
    &\quad W_1 \nequal W_2 \land W_1' \futurewk W_1 \Rightarrow \exists W_2' \ldotp W_2' \nequal W_1' \land W_2' \futurewk W_2
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:wk-nequal-and-future}]
  Construct $W_2'$ as follows:
  \[
    W_2(r) =
    \begin{cases}
      (v_1',s_1',\phi_{\pub2},\phi_2,H_2) & \arraycolsep=0pt
      \begin{array}[t]{l}
        \text{ if $r \in \dom(W_2)$ and $W_1'(r) = (v_1',s_1',\_,\_,\_)$}\\
        \quad \text{ and $W_2(r) = (\_,\_,\phi_{\pub2},\phi_2,H_2)$}\\
      \end{array} \\
      W_1'(r) & \text{ otherwise}
    \end{cases}
  \]
  Notice $\dom(W_2') = \dom(W_1')$.
\end{proof}

\begin{lemma}
  \label{lem:str-nequal-and-future}
  \begin{align*}
    &\forall n,W_1,W_2,W_1' \ldotp
    &\quad W_1 \nequal W_2 \land W_1' \futurestr W_1 \Rightarrow \exists W_2' \ldotp W_2' \nequal W_1' \land W' \futurestr W_2
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:str-nequal-and-future}]
  Construct $W_2'$ as follows:
  \[
    W_2(r) =
    \begin{cases}
      (v_1',s_1',\phi_{\pub2},\phi_2,H_2) & \arraycolsep=0pt
      \begin{array}[t]{l}
        \text{ if $r \in \dom(W_2)$ and $W_1'(r) = (v_1',s_1',\_,\_,\_)$}\\
        \quad \text{ and $W_2(r) = (\_,\_,\phi_{\pub2},\phi_2,H_2)$}\\
      \end{array} \\
      W_1'(r) & \text{ otherwise}
    \end{cases}
  \]
